### 2020-12-14 paper/sections/experiment.tex
major abstract

\subsection{Experiment Setup and Configuration Selection}
\label{subsec: configuration}
We carry out real-world experiments on the object detection task (basic computer vision services) to verify our solution’s performance. We use a desktop PC (Intel Xeon E5-2650 v4 CPU) with four NVIDIA 1080ti graphic card as the server infrastructure, and simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2. For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up. In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. We use FFmpeg to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model. The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
%In the service inference, the processing video module uses CPU resources, and the object detection module uses GPU resources. In our study, we use GPU processing time as the metric of resource consumption because GPU is the dominant resource for most video processing workloads \cite{jiang2018chameleon}.In the evaluation, the processing video module needs 62s to decode 5 mins video into 9000 frames image (i.e., average CPU processing time per frame is about 0.006s), which is lower than the GPU processing time. To reduce the latency of processing video, we use different processes to carry out the processing video module and the object detection module in our experiments.

\subsection{Dataset and Metric}
\label{subsec: datasets}
Most public sources datasets cannot fully satisfy all configuration choices, they provide only a fraction of the requirements for configuration. %for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution. In contrast, others can ensure resolution but cannot provide a sufficient frame rate. 
%In recent years, most of the driving recorder can provide enough resolution and frame rate, so 
We try to search keywords (e.g., ``highway traffic'') on Youtube and download videos that meet the resolution and frame rate requirements. We selecte three datasets: M6, Duke, and Multi-Camera Dataset. M6 is taken from a traffic camera on the longest motorway in Britain. Duke is a video from a fixed camera placed at an intersection, and the traffic flow in the video increases or decreases periodically with the traffic light change. 
%Since the first two datasets were sourced from a fixed camera, 
To ensure that AdaConfigure performs better in multi-camera inference, we combine three videos collected from different locations into one video dataset, Multi-Camera Dataset. The exact content of this dataset varies significantly over time and across space.

@@

\begin{table}[!t]
	\centering
	%     \begin{tabular}{llllll}
	\resizebox{0.4\textwidth}{!}{
		\begin{tabular}{cccccc}
			\toprule
			Notation          & Value & & & Notation     & Value  \\ \midrule
			$\epsilon$    & 0.8    & & & $k_1$      & 3   \\
			$\gamma$      & 0.9  & & & $k_2$    & 3    \\
			$ \beta $ & 0.2,0.3,...,0.7 & & & $ T (train) $ & 1  \\
			$ t(inference)  $  &  1   & & &   $ T (inference)  $  &  4      \\ 
			\bottomrule
	\end{tabular}}
	\caption{Experiment parameters}
	\label{tab: parameters}
%	\vspace{-0.5cm}
\end{table}

@@

\subsubsection{Low Profiling Cost of Adaptive Configuration}
\label{subsec: profiling cost}
%Comparing to the static solution that profiles configurations once, in our solution, the video
%chunk is passed to the AdaConfigure firstly to estimate the configuration. Running this RL agent brings profiling cost (extra resource consumption) to the whole system. 
%In this section, we evaluate this profiling cost. 
%In the inference phase, we divide the video into $T$-second intervals as video chunks and use AdaConfigure to choose the proper configuration for the first t seconds of the video chunk. It then sticks with the chosen configuration for the rest of the video chunk, i.e., for $T-t$ seconds. We use T = 4 and t = 1 for our experiments.
In our solution, the video chunk is passed to the AdaConfigure firstly to estimate the configuration, bringing profiling cost (extra resource consumption) to the whole system. 
The profiling cost, including the resource of extract $k_1$ embeddings and the cost of agent choosing actions. We test the average time on 30 hours video of Multi-Camera Dataset, and conclude that the average time of extract one embedding is 0.02s, and the average time of agent choosing action is 0.0006s, which can be ignored. We compute the ratio by dividing profiling time into total inference time as metric of profiling cost.
%, which is equals the frame number multiply the average time per frame. 
The profiling cost is about 0.2-2\% of the overall video analytics resource consumption. The concrete ratio depends on the concrete AdaConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}. For instance, when using the $\beta$ 0.7 solution, the profiling time is only 0.2\% of overall resource consumption on this solution; when using the $\beta$ 0.2 solution, the profiling cost is 1.5\%.

@@

\begin{table}[!t]
	\centering
	%     \begin{tabular}{lll}
	\resizebox{0.4\textwidth}{!}{
		\begin{tabular}{ccc}
			\toprule
			balance factor $\beta$ & Avg GPU time per frame (second) & Avg F1 score  \\ \midrule
			0.2          & 0.01384  &  0.64307            \\
			0.3          & 0.03314  &  0.72008            \\
			0.4          & 0.05203  &  0.79096            \\
			0.5          & 0.08479  &  0.80056            \\
			0.6          & 0.17570  &  0.87731            \\
			0.7          & 0.26511  &  0.93262            \\
			\bottomrule
	\end{tabular}}
	\caption{Resource consumption and bounding box-based F1 for different AdaConfigure solutions}
	\label{tab: different sulutions}
	%	\vspace{-0.1cm}
\end{table}

>>>>

\subsection{Experiment Setup}
\label{subsec: configuration}
We carry out real-world experiments on the object detection task (basic computer vision services) to verify our solution’s performance. We use a desktop PC (Intel Xeon E5-2650 v4 CPU) with four NVIDIA 1080ti graphic card as the server infrastructure, and simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2. For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up. In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. We use FFmpeg to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model. The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total.
%In the service inference, the processing video module uses CPU resources, and the object detection module uses GPU resources. In our study, we use GPU processing time as the metric of resource consumption because GPU is the dominant resource for most video processing workloads \cite{jiang2018chameleon}.In the evaluation, the processing video module needs 62s to decode 5 mins video into 9000 frames image (i.e., average CPU processing time per frame is about 0.006s), which is lower than the GPU processing time. To reduce the latency of processing video, we use different processes to carry out the processing video module and the object detection module in our experiments.

\subsection{Datasets and Metric}
\label{subsec: datasets}
Most public sources datasets cannot fully satisfy all configuration choices, they provide only a fraction of the requirements for configuration. %for example, some can only guarantee 30 frames but cannot guarantee 1024p resolution. In contrast, others can ensure resolution but cannot provide a sufficient frame rate. 
%In recent years, most of the driving recorder can provide enough resolution and frame rate, so 
We try to search keywords (e.g., ``highway traffic'') on Youtube and download videos that meet the resolution and frame rate requirements. We selecte three datasets: M6, Duke, and Multi-Camera Dataset. M6 is taken from a traffic camera on the longest motorway in Britain. Duke is a video from a fixed camera placed at an intersection, and the traffic flow in the video increases or decreases periodically with the traffic light change. 
%Since the first two datasets were sourced from a fixed camera, 
To ensure that AdaConfigure performs better in multi-camera inference, we combine three videos collected from different locations into one video dataset, Multi-Camera Dataset. The exact content of this dataset varies significantly over time and across space.

@@

\begin{table}[!t]
	\centering
	%     \begin{tabular}{llllll}
	\resizebox{0.45\textwidth}{!}{
		\begin{tabular}{cccccc}
			\toprule
			Notation          & Value & & & Notation     & Value  \\ \midrule
			$\epsilon$    & 0.8    & & & $k_1$      & 3   \\
			$\gamma$      & 0.9  & & & $k_2$    & 3    \\
			$ \beta $ & 0.2,0.3,...,0.7 & & & $ T (train) $ & 1  \\
			$ t(inference)  $  &  1   & & &   $ T (inference)  $  &  4      \\ 
			\bottomrule
	\end{tabular}}
	\caption{Experiment parameters}
	\label{tab: parameters}
%	\vspace{-0.5cm}
\end{table}

@@

\subsubsection{Low Profiling Cost of Adaptive Configuration}
\label{subsec: profiling cost}
%Comparing to the static solution that profiles configurations once, in our solution, the video
%chunk is passed to the AdaConfigure firstly to estimate the configuration. Running this RL agent brings profiling cost (extra resource consumption) to the whole system. 
%In this section, we evaluate this profiling cost. 
%In the inference phase, we divide the video into $T$-second intervals as video chunks and use AdaConfigure to choose the proper configuration for the first t seconds of the video chunk. It then sticks with the chosen configuration for the rest of the video chunk, i.e., for $T-t$ seconds. We use T = 4 and t = 1 for our experiments.
In our solution, the video chunk is passed to the AdaConfigure firstly to estimate the configuration, bringing profiling cost (extra resource consumption) to the whole system. 
The profiling cost, including the resource of extract $k_1$ embeddings and the cost of agent choosing actions. We test the average time on 30 hours video of Multi-Camera Dataset, and conclude that the average time of extract one embedding is 0.02s, and the average time of agent choosing action is 0.0006s, which can be ignored. We compute the ratio by dividing profiling time into total inference time as metric of profiling cost.
%, which is equals the frame number multiply the average time per frame. 
The profiling cost is about 0.2-2\% of the overall video analytics resource consumption. The concrete ratio depends on the concrete AdaConfigure configuration solutions, such as the solutions listed in Table \ref{tab: different sulutions}. For instance, when using the $\beta$ 0.7 solution, the profiling cost is only 0.2\% of overall resource consumption on this solution; when using the $\beta$ 0.2 solution, the profiling cost is 1.5\%.

@@

\begin{table}[!t]
	\centering
	%     \begin{tabular}{lll}
	\resizebox{0.45\textwidth}{!}{
		\begin{tabular}{ccc}
			\toprule
			balance factor $\beta$ & Avg GPU time per frame (second) & Avg F1 score  \\ \midrule
			0.2          & 0.01384  &  0.64307            \\
			0.3          & 0.03314  &  0.72008            \\
			0.4          & 0.05203  &  0.79096            \\
			0.5          & 0.08479  &  0.80056            \\
			0.6          & 0.17570  &  0.87731            \\
			0.7          & 0.26511  &  0.93262            \\
			\bottomrule
	\end{tabular}}
	\caption{Resource consumption and bounding box-based F1 for different AdaConfigure solutions}
	\label{tab: different sulutions}
	%	\vspace{-0.1cm}
\end{table}

### 2020-12-14 paper/sections/introduction.tex
major abstract

Different configurations directly affect accuracy and resource consumption. The best configuration is the one with the lowest resource demand whose accuracy is over the desired threshold, whcih can optimize the \emph{trade-off} between accuracy and energy consumption. The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}. As shown in Figure~\ref{fig: framework}(a), if one just uses a fixed static expensive configuration (e.g., only profiles the processing pipeline \emph{once} to choose high frame rate and resolution) can be very precise, but it can also be a huge drain on resource consumption. Similarly, specifying a fixed static cheap configuration (e.g., low resolution and small model) will significantly reduce accuracy. The framework of our solution %To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework
is shown in Figure~\ref{fig: framework}(b), and we tackle the following design challenges.

\begin{figure*}[!t]
	%\begin{tabular}{cc}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.9\linewidth]{figures/static_framework.pdf}}
		\begin{center}
			{(a) Static configuration solution: fixed configuration for video analytics services}
		\end{center}
		%        \vspace{0.3cm}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.9\linewidth]{figures/auto_framework.pdf}}
		\vspace{0.2cm}
		\begin{center}
			{(b) AdaConfigure solution: reinforcement learning-based adaptive configuration framework}
		\end{center}
	\end{minipage}
	%\end{tabular}
	%\vspace{0.1cm}
	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the object detection model feedback}
	%	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
	\label{fig: framework}
	\vspace{-0.5cm}
\end{figure*}

\setlist{nolistsep}
\begin{itemize}	
	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to be solved by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space. For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly. Spatially, the characteristics of video content are different in different locations. For instance, cameras in downtown areas show more cars than the other cameras deployed in the suburbs. It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video characteristics.
%	but each condition may vary by hour, minute, even second.
	%As a dynamic video analytics configuration %solution
	%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video contexts, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

	\item \emph{Adaptive configuration would cause a huge extra overhead.} %The number of possible configurations grows exponentially, 
	There are thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}. So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations. To significantly reduce the resource cost for adaptive configuration requires one solution that automatically choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{jiang2018chameleon,wang2020jcab}, since their approaches pay attention to reduce search space algorithm and still try using various configurations to find the best configuration.

	%We leverage a Reinforcement Learning-based agent to adaptively pick the best configuration periodically, dramatically reducing the profiling cost. 
	%How to significantly reduce the resource cost of periodic configuration profiling.

	%\item \emph{Lack of well-labeled training data.} In our case, there was no well-marked data that indicated which configuration should be choosed at which time of the video, as is the case with traditional deep learning tasks.%In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks. In practice, such a video analytics configuration is usually utilized online, and the solution has to adaptively learn from the video contexts. 
\end{itemize}
\setlist{nolistsep}
%To address the above problems, 
%To address the above complicated decision-making problem and reduce the huge extra overhead of manually trying using various configurations,
%We carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem. 
In our solution, AdaConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video contexts, thus solving this difficult optimal configuration decision problem in a low-cost way. To the best of our knowledge, we are the first to propose an adaptive video configuration solution for such problems. 
%that adaptively and automatically chooses a configuration according to the current video context. 
The main contributions of this paper are summarized as follows.

\begin{itemize}	
	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to the characteristics of the video stream. For the agent's state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation. 
	\item We leverage a video segmentation strategy and agent's automatic selection characteristic to reduce profiling cost. In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk. It then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds).
%to capture the characteristics of the video stream with much-reduced computation cost: profiling a segment uses only 0.2-2\% computation resource as compared to a full video.
%	Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.
%the extremely short choosing action time of agent
	\item We design a reward function that carefully considers both inference accuracy and computation resources to assess each configuration's impact. Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents. Our solution can adaptively update configuration strategy over time, and it is adaptive to different location-camera inferences and different accuracy-demand services.
% 	First, we design a reinforcement learning-based framework in which an agent adaptively chooses the configuration according to the spatial and temporal features of the current video stream.
	%	 We design an interactive training environment that can be applied to different video analytics applications.
	%	\item We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analytics after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.

%	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost. In the evaluation, AdaConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources. Our solution proves to be more efficient than static solutions and only creates an overhead of 0.2-2\% to the overall video analytics services.

%	\item Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 60-90% of the computation resource. 
\end{itemize}

>>>>

Different configurations directly affect accuracy and resource consumption. The best configuration is the one with the lowest resource demand whose accuracy is over the desired threshold, whcih can optimize the \emph{trade-off} between accuracy and energy consumption. The \emph{best} configuration for video analysis services often varies in minutes or even seconds \cite{jiang2018chameleon}. As shown in Figure~\ref{fig: framework}(a), if one uses an expensive static configuration (e.g., only profiles the processing pipeline \emph{once} to choose the high frame rate and image resolution) can be precise, but it can also be a huge drain on resource consumption. Similarly, specifying a cheap static configuration (e.g., low resolution and small model) will significantly reduce accuracy. The framework of our solution %To tackle these challenges, we propose an adaptive configuration approach, AdaConfigure, and the brief framework
is shown in Figure~\ref{fig: framework}(b), and we tackle the following design challenges.

\begin{figure*}[!t]
	%\begin{tabular}{cc}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.9\linewidth]{figures/static_framework.pdf}}
		\begin{center}
			{(a) Static configuration solution: fixed configuration for video analytics services}
		\end{center}
		%        \vspace{0.3cm}
	\end{minipage}
	\vfill
	\vspace{0.4cm}
	\begin{minipage}{\linewidth}
		\centerline{\includegraphics[width=0.9\linewidth]{figures/auto_framework.pdf}}
		\vspace{0.2cm}
		\begin{center}
			{(b) AdaConfigure solution: reinforcement learning-based adaptive configuration framework}
		\end{center}
	\end{minipage}
	%\end{tabular}
	%\vspace{0.1cm}
	\caption{Comparing to the static solution, our solution can adaptively update the configuration strategy based on the reward feedback}
	%	\caption{Comparing to the static solution, our solution can update the configuration strategy based on the object detection model feedback}
	\label{fig: framework}
	\vspace{-0.5cm}
\end{figure*}

\emph{Choosing the best configuration is a complicated decision-making problem that is challenging to be solved by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space. For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly. Spatially, the characteristics of video content are different in different locations. For instance, cameras in downtown areas show more cars than the other cameras deployed in the suburbs. It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video characteristics.
%	but each condition may vary by hour, minute, even second.
%As a dynamic video analytics configuration %solution
%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video context, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.

\emph{Adaptive configuration would cause a huge extra overhead.} The number of possible configurations grows exponentially, and thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}. So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations. To significantly reduce the resource cost for adaptive configuration requires one solution that automatically chooses a configuration instead of manually trying using various configurations, which is challenging to previous studies including \cite{jiang2018chameleon,wang2020jcab}, since their approaches pay attention to reduce search space algorithm, and try various configurations in search space to find the best configuration.
%using a brute-force search (i.e., periodically trying various configurations and selecting the one with the best performance)

%\setlist{nolistsep}
%\begin{itemize}	
%	\item \emph{Choosing the best configuration is a complicated decision-making problem that is challenging to be solved by rules.} The best configuration for video analytics services changes significantly because the exact context of the videos varies over time and across space. For instance, tracking vehicles when traffic moves quickly requires a higher frame rate than when traffic moves slowly. Spatially, the characteristics of video content are different in different locations. For instance, cameras in downtown areas show more cars than the other cameras deployed in the suburbs. It is hard to make an exact rule to choose a configuration for the current context by profiling such complicated video characteristics.
%%	but each condition may vary by hour, minute, even second.
%	%As a dynamic video analytics configuration %solution
%	%application, we target to provide a solution that dynamically picks a configuration according to intrusive dynamics of video context, i.e., it can \emph{generate} video analytics configuration for video analytics in a different time.
%	
%	\item \emph{Adaptive configuration would cause a huge extra overhead.} %The number of possible configurations grows exponentially, 
%	There are thousands of configurations can be combined with just a few knobs \cite{jiang2018chameleon}. So exhaustive periodically (e.g., profile once per 4 seconds) configuration to find the best configuration is a highly unrealistic approach because it causes a huge extra overhead, which may exceed the benefits of adaptive configurations. To significantly reduce the resource cost for adaptive configuration requires one solution that automatically choose a configuration instead of manually trying using various configurations, which is challengling to previous studies including \cite{jiang2018chameleon,wang2020jcab}, since their approaches pay attention to reduce search space algorithm and still try using various configurations to find the best configuration. 
%	
%	%We leverage a Reinforcement Learning-based agent to adaptively pick the best configuration periodically, dramatically reducing the profiling cost. 
%	%How to significantly reduce the resource cost of periodic configuration profiling.
%	
%	%\item \emph{Lack of well-labeled training data.} In our case, there was no well-marked data that indicated which configuration should be choosed at which time of the video, as is the case with traditional deep learning tasks.%In our problem, one is not provided the well-labeled data on which configuration should be used in which time of the video, as in conventional supervised deep learning tasks. In practice, such a video analytics configuration is usually utilized online, and the solution has to adaptively learn from the video context. 
%\end{itemize}
%\setlist{nolistsep}

%To address the above problems, 
%To address the above complicated decision-making problem and reduce the huge extra overhead of manually trying using various configurations,
%We carefully design an adaptive configuration framework based on reinforcement learning, which is an excellent approach to solve this unsupervised complex-environmental problem. 
In our solution, AdaConfigure can adaptively and automatically select the best configuration according to intrusive dynamics of video context, thus solving this difficult optimal configuration decision problem in a low-cost way. To the best of our knowledge, we are the first to propose an adaptive video configuration solution for such problems. 
%that adaptively and automatically chooses a configuration according to the current video context. 
The main contributions of this paper are summarized as follows.

We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to the characteristics of the video stream. For the agent's state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation.

We leverage  agent's automatic selection characteristic and the video segmentation strategy to reduce profiling cost. In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk. It then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds) to reduce profiling number. In the evaluation, the profiling cost is about 0.2-2\% of the overall video analytics resource consumption.

We design a reward function that considers both inference accuracy and computation resources to assess each configuration's impact. Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents. Our solution can adaptively update configuration strategy over time, and it is adaptive to different location-camera inferences and different accuracy-demand services. Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 50-90\% of the computation resource.

%\begin{itemize}	
%	\item We propose a Deep Q-learning Network-based \cite{DQN} agent to adaptively pick the best video analytics configuration according to the characteristics of the video stream. For the agent's state, we extract the spatial and temporal features of the video context, so that the agent can adaptively update configuration over time and achieve a superior performance in the multi-camera situation. 
%	\item We leverage  agent's automatic selection characteristic and the video segmentation strategy to reduce profiling cost. In particular, we divide the video into $T$-second intervals as video chunks and use the agent to choose the best configuration for the first t seconds of the video chunk. It then sticks with the chosen configuration for the rest of the video chunk ($T-t$ seconds) to reduce profiling number. In the evaluation, the profiling cost is about 0.2-2\% of the overall video analytics resource consumption. 
%%to capture the characteristics of the video stream with much-reduced computation cost: profiling a segment uses only 0.2-2\% computation resource as compared to a full video.
%%	Also, we define the elements of the RL-based approach, such as actions, states, and rewards, to decide the configuration for the current video context.
%%the extremely short choosing action time of agent
%	\item We design a reward function that considers both inference accuracy and computation resources to assess each configuration's impact. Also, to meet different accuracy-demand services, we leverage the balance factor in the reward function to train different agents. Our solution can adaptively update configuration strategy over time, and it is adaptive to different location-camera inferences and different accuracy-demand services. Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 50-90\% of the computation resource.
%% 	First, we design a reinforcement learning-based framework in which an agent adaptively chooses the configuration according to the spatial and temporal features of the current video stream.
%	%	 We design an interactive training environment that can be applied to different video analytics applications.
%	%	\item We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a ``most appropriate'' configuration for each timestamp of video analytics after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and resources.
%	
%%	\item We leverage dividing video strategy and the extremely short choosing action time of agent to reduce profiling cost. In the evaluation, AdaConfigure achieves 10-35\% higher accuracy with a similar amount of resources or achieves similar accuracy with only 60-90\% of the resources. Our solution proves to be more efficient than static solutions and only creates an overhead of 0.2-2\% to the overall video analytics services.
%	
%%	\item Our evaluation experiments on object detection task show that our approach outperforms baseline: it achieves 10-35\% higher accuracy with a similar amount of computation resources or achieves similar accuracy with only 60-90% of the computation resource. 
%\end{itemize}

### 2020-12-14 paper/sections/relatedwork.tex
major abstract

%\subsection{Configuration optimization} 
\subsection{Static Configuration Optimization}
Several previous papers have considered optimizing video analytics services by either adjusting the configuration knobs or training specialized NN models. VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations. VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations. 
%MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints. 
Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingests and video query. By tuning the share of computing resources of both phases, Focus achieves an effective and flexible tradeoff of video analytics's latency and accuracy. These algorithms all profile and optimize video analytics only once at the beginning of the video. In their works, video is divided into pictures at a constant frame rate, and the work of video analysis is regarded as a fixed task either. In other words, they do not handle changes in video stream context. But the optimal configurations do change over time because of the complex and changeable video stream contexts.

\subsection{Dynamic Configuration Optimization}
%Some classic works study dynamic optimization problems. INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations and makes scaling and resource allocation decisions when application load varies and the available resources vary over time. QuickAdapt \cite{ullah2019quickadapt} uses descriptive statistics of security events data and fuzzy rules to enable a Big Data Cyber Security Analytics (BDCA) system to adapt to the changes in security events data quickly. 
Some papers study how to dynamically optimize the configuration for video analytics when the video stream context changes. JCAB \cite{wang2020jcab} jointly optimizes configuration adaption, and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video contexts. Chameleon \cite{jiang2018chameleon} leverages temporal and spatial correlation to decrease the cost of profiling over time, and exploits the knob independence to reduce the search space from exponential to linear. Notice these reduce search space algorithms still try using various configurations to find the best configuration. Using different configurations lead to extra expensive profiling costs. To significantly reduce the cost of profiling, we propose an automatic and adaptive configuration algorithm. \cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider inference latency. Our framework pays attention to the characteristics of the video stream and picks the best configuration according to the spatial and temporal features of the current video stream.

>>>>

%\subsection{Configuration optimization} 
\subsection{Static Configuration Optimization}
Several previous papers have considered optimizing video analytics services by either adjusting the configuration knobs or training specialized NN models. VideoStorm \cite{zhang2017videostorm} profiles thousands of video analytics queries on live video streams over large clusters, achieving resource-quality tradeoff with multi-dimensional configurations. VideoEdge \cite{hung2018videoedge} introduces \emph{dominant demand} to identify the best tradeoff between multiple resources and accuracy, and narrows the search space by identifying a ``Pareto ban'' of promising configurations. MCDNN \cite{han2016mcdnn} provides a heuristic scheduling algorithm to adaptively select model variants of different accuracy for deep stream processing under resource constraints. Focus \cite{hsieh2018focus} deconstructs video analytics into two phases (i.e., video ingests and video query), achieving an effective and flexible tradeoff of video analytics's latency and accuracy. These algorithms all profile and optimize video analytics only once at the beginning of the video. In their works, video is divided into pictures at a constant frame rate, and the work of video analysis is regarded as a fixed task either. In other words, they do not handle changes in video stream context. But the optimal configurations do change over time because of the complex and changeable video stream context.

%Focus \cite{hsieh2018focus} deconstructs video analytics into two phases, i.e., video ingests and video query. By tuning the share of computing resources of both phases, Focus achieves an effective and flexible tradeoff of video analytics's latency and accuracy.

\subsection{Dynamic Configuration Optimization}
%Some classic works study dynamic optimization problems. INFaaS \cite{romero2019infaas} automatically selects a model, hardware architecture, and any compiler optimizations and makes scaling and resource allocation decisions when application load varies and the available resources vary over time. QuickAdapt \cite{ullah2019quickadapt} uses descriptive statistics of security events data and fuzzy rules to enable a Big Data Cyber Security Analytics (BDCA) system to adapt to the changes in security events data quickly. 
Some papers study how to dynamically optimize the configuration for video analytics when the video stream context changes. JCAB \cite{wang2020jcab} jointly optimizes configuration adaption, and bandwidth allocation to address several critical challenges in edge-based video analytics systems, including edge capacity limitation, unknown network variation, intrusive dynamics of video context. Chameleon \cite{jiang2018chameleon} leverages temporal and spatial correlation to decrease the cost of profiling, and exploits the knob independence to reduce the search space from exponential to linear. Notice these reduce search space algorithms still trying various configurations to find the best configuration. Using different configurations lead to extra expensive profiling costs. To significantly reduce the cost of profiling, we propose an automatic and adaptive configuration algorithm. \cite{argerich2019orchestration} leverages tabular Q-learning to adapt configuration, but their agent's states only consider inference latency. Our framework pays attention to the characteristics of the video stream and picks the best configuration according to the spatial and temporal features of the current video stream.
